---
title: "Regression_cars"
author: "Harsh Singh"
date: "8/18/2019"
---
## Printing first 6 rows of car dataset  

```{r}
head(cars)

```

## Plotting a scatter plot to understand the relationship between the predictor and response variables. The scatter plot indicates a linearly increasing relationship between the two variable.


```{r}
attach(cars)
scatter.smooth(speed,dist,main="Dist ~ Speed")
```

## Spotting any outlier observations in the variable by plotting a box plot. We begin by dividing the graph are into two coloumns. One coloumnm contains the box plot for "speed" and the second coloumn contains the box plot for "distance". 

```{r}
par(mfrow=c(1,2))
boxplot(speed,main="Speed",sub=paste("Outlier rows:",boxplot.stats(speed)$out))
boxplot(dist,main="Distance",sub=paste("Outlier rows:",boxplot.stats(dist)$out))
```
##Building a relationshop model. The "coefficients" part has two components, "Intercept" and "speed". These are also called the beta coeefecients. In other words, dist = intercept + beta*speed  

```{r}
LinearMod <- lm(dist ~ speed, data = cars)
print(LinearMod)
```
##printing summary of built linear model

```{r}
print(summary(LinearMod))
```
##Visulaising the regression graphically by plotting  a chart
```{r}
plot(dist,speed,col = "blue",main="Speed & Distance Regression",abline(lm(speed ~ dist)),cex = 1.3,pch=16,xlab ="Distance",ylab = "Speed")
```
